Omics-based Single Step Trait Prediction

### 2017-09-15 paper/manuscript.tex
paper, init abstract

\begin{abstract}

  $\dots$

\end{abstract}

>>>>

\begin{abstract}
Predicting the performance of candidates is indispensable for selection
decisions in animal and plant breeding.
Novel `omics' predictors have shown to improve upon genomics-based predictions
of some complex traits but are yet expensive to sample.
Here we show that single step prediction can be applied to a quantitative
predictor.

Using two maize datasets of inbred lines and hybrids we show that transcriptomic
data can successfully be imputed, boosting forecasts when their predictive
ability exceeds that of pedigree or genomic data.

Equipping only a subset of genotypes with `omics' predictors and imputing all
others using pedigree or genomic data could enable breeders to improve trait
predictions while keeping costs manageable.
Employing `omics' predictors could particularly benefit candidate selection in
hybrid breeding.
\end{abstract}
